### 2021-08-06 paper/paper.tex
describe reproducibility material in the main README.md and clean up folders

\begin{figure}[!ht]
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (seconds)},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.0e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_euler_weak.dat};
          \addlegendentry{FLUXO}
%         \addplot[orange, mark=square*, solid] % TreeMesh, weak form
%           table [x index=0, y index=1]{../data/pids_euler_weak.dat};
%           \addlegendentry{\texttt{TreeMesh} (\trixi)}
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_euler_weak.dat};
          % \addlegendentry{\texttt{StructuredMesh} (\trixi)}
          \addlegendentry{\trixi}
        \node at (axis cs:13,3.5e-7) {Weak form};

        \addplot[blue, mark=*, dashed] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_euler_ranocha.dat};
%         \addplot[orange, mark=square*, dashed] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_euler_ranocha.dat};
        \node [rotate=15] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:8.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.4, 0.5, 0.6, 0.8, 1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_euler_weak_relative.dat};
%         \addplot[orange, mark=square*, solid, forget plot] % TreeMesh, weak form
%           table [x index=0, y index=1]{../data/pids_euler_weak_relative.dat};
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_euler_weak_relative.dat};
          \addlegendentry{Weak form}

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

\begin{figure}[!ht]
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.0e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_weak.dat};
          \addlegendentry{FLUXO}
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_weak.dat};
          \addlegendentry{\trixi}
        \node [rotate=12] at (axis cs:13.5,5.75e-7) {Central flux};
        \draw (axis cs:13,6.0e-7) -- (axis cs:12.4,7.1e-7);
        \draw (axis cs:13.4,6.3e-7) -- (axis cs:13.7,1.075e-6);

        \addplot[blue, mark=*, dashed] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_flogor.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_flogor.dat};
        \node [rotate=20] at (axis cs:7,1.2e-6) {EC flux};
        \draw (axis cs:8.4,1.1e-6) -- (axis cs:7.75,1.15e-6);
        \draw (axis cs:7,1.1e-6) -- (axis cs:7.5,6.5e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.5, 0.6, 0.7, 0.8, 0.9, 1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_weak_relative.dat};
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_weak_relative.dat};
          \addlegendentry{Central flux}

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_flogor_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_flogor_relative.dat};
          \addlegendentry{EC flux}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           the flux differencing DG discretization of the 3D ideal MHD equations.
           Two configurations are compared using either the central volume flux
           (algebraically equivalent to the weak form DG solver) and the entropy
           conservative (EC) volume flux.}
  \label{fig:PID-MHD}
\end{figure}

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the Intel was between $5\%$ to $23\%$ faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational overhead for the entropy conservative, flux
differencing DG methods for both physical models. This is because the numerical fluxes are more complex, in
terms of computational effort, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

Note that we do not want to state that Julia is generically faster than Fortran,
C, or C++. In contrast, we would like to emphasize that Julia can be at least
as fast as code written in these traditional scientific computing languages.
%We believe that it will be possible to get the same efficiency by rewriting
%FLUXO appropriately.
Together, the members of our team have strong backgrounds in C, C++, and
Fortran. Nevertheless, our Julia code is faster than the established HPC Fortran
code FLUXO for this example. The reason is not that Fortran or Julia are generically
faster; in contrast, we expect to be able to achieve similar performance from either
language. Instead, \trixi owes its performance optimizations in part to the code
introspection and profiling tools available in Julia. Similar tools used to optimize the
performance in other languages are usually not as easy to use as their Julia
equivalents (if they exist at all).

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the relative computational effort of the discretization
(such as the polynomial degree and the choice of the volume terms), the
Cartesian \lstinline{TreeMesh} can be \ca \SI{10}{\percent}--\SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.

>>>>

\begin{figure}[!ht]
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (seconds)},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.0e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid] % FLUXO, weak form
          table [x index=0, y index=2]{../pid_data/pids_euler_weak.dat};
          \addlegendentry{FLUXO}
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../pid_data/pids_euler_weak.dat};
          \addlegendentry{\trixi}
        \node at (axis cs:13,3.5e-7) {Weak form};

        \addplot[blue, mark=*, dashed] % FLUXO, flux differencing
          table [x index=0, y index=2]{../pid_data/pids_euler_ranocha.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../pid_data/pids_euler_ranocha.dat};
        \node [rotate=15] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:8.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.4, 0.5, 0.6, 0.8, 1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot] % FLUXO, weak form
          table [x index=0, y index=2]{../pid_data/pids_euler_weak_relative.dat};
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../pid_data/pids_euler_weak_relative.dat};
          \addlegendentry{Weak form}

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../pid_data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../pid_data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

\begin{figure}[!ht]
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.0e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid] % FLUXO, weak form
          table [x index=0, y index=2]{../pid_data/pids_mhd_weak.dat};
          \addlegendentry{FLUXO}
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../pid_data/pids_mhd_weak.dat};
          \addlegendentry{\trixi}
        \node [rotate=12] at (axis cs:13.5,5.75e-7) {Central flux};
        \draw (axis cs:13,6.0e-7) -- (axis cs:12.4,7.1e-7);
        \draw (axis cs:13.4,6.3e-7) -- (axis cs:13.7,1.075e-6);

        \addplot[blue, mark=*, dashed] % FLUXO, flux differencing
          table [x index=0, y index=2]{../pid_data/pids_mhd_flogor.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../pid_data/pids_mhd_flogor.dat};
        \node [rotate=20] at (axis cs:7,1.2e-6) {EC flux};
        \draw (axis cs:8.4,1.1e-6) -- (axis cs:7.75,1.15e-6);
        \draw (axis cs:7,1.1e-6) -- (axis cs:7.5,6.5e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.5, 0.6, 0.7, 0.8, 0.9, 1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot] % FLUXO, weak form
          table [x index=0, y index=2]{../pid_data/pids_mhd_weak_relative.dat};
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../pid_data/pids_mhd_weak_relative.dat};
          \addlegendentry{Central flux}

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../pid_data/pids_mhd_flogor_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../pid_data/pids_mhd_flogor_relative.dat};
          \addlegendentry{EC flux}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           the flux differencing DG discretization of the 3D ideal MHD equations.
           Two configurations are compared using either the central volume flux
           (algebraically equivalent to the weak form DG solver) and the entropy
           conservative (EC) volume flux.}
  \label{fig:PID-MHD}
\end{figure}

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the Intel was between \SI{5}{\percent} to \SI{23}{\percent} faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational overhead for the entropy conservative, flux
differencing DG methods for both physical models. This is because the numerical fluxes are more complex, in
terms of computational effort, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

Note that we do not want to state that Julia is generically faster than Fortran,
C, or C++. In contrast, we would like to emphasize that Julia can be at least
as fast as code written in these traditional scientific computing languages.
Together, the members of our team have strong backgrounds in C, C++, and
Fortran. Nevertheless, our Julia code is faster than the established HPC Fortran
code FLUXO for this example. The reason is not that Fortran or Julia are generically
faster; in contrast, we expect to be able to achieve similar performance from either
language. Instead, \trixi owes its performance optimizations in part to the code
introspection and profiling tools available in Julia. Similar tools used to optimize the
performance in other languages are usually not as easy to use as their Julia
equivalents (if they exist at all).

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the relative computational effort of the discretization
(such as the polynomial degree and the choice of the volume terms), the
Cartesian \lstinline{TreeMesh} can be \ca \SI{10}{\percent} to \SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.
